|

### 2024-08-10 doc/paper.qmd
em3

### Smoothing Reported Operating Earnings Using Accruals (EM1) {#sec-EM1}
`EM1` is a measure that assesses how much insiders (e.g., company executives) smooth or stabilize reported earnings by manipulating accruals. The concept is that firms may attempt to reduce fluctuations in their reported operating income to present a more stable financial performance to investors. This measure reflects the degree to which insiders use accounting discretion to smooth reported earnings, with lower values of EM1 suggesting more extensive earnings smoothing.

@@

### Smoothing and the Correlation Between Changes in Accounting Accruals and Operating Cash Flows (EM2)
`EM2` is designed to capture the extent to which insiders use accounting discretion to smooth reported earnings by examining the correlation between changes in accruals and changes in operating cash flows. A stronger negative correlation between these variables indicates that accruals are being used to buffer the impact of cash flow fluctuations, potentially masking the true economic performance of the firm.

@@

4. Calculate EM2, which is computed as the Spearman correlation between these scaled changes, aggregated at the country level:
$$
\text{EM2} = \rho\left(\frac{\Delta \text{Accruals}_{it}}{\text{Total Assets}_{i(t-1)}}, \frac{\Delta \text{CFO}_{it}}{\text{Total Assets}_{i(t-1)}}\right)
$$

### Discretion in Reported Earnings: The Magnitude of Accruals (EM3)

>>>>

### Smoothing Reported Operating Earnings Using Accruals (EM1) {#sec-EM1}
EM1 is a measure that assesses how much insiders (e.g., company executives) smooth or stabilize reported earnings by manipulating accruals. The concept is that firms may attempt to reduce fluctuations in their reported operating income to present a more stable financial performance to investors. This measure reflects the degree to which insiders use accounting discretion to smooth reported earnings, with lower values of EM1 suggesting more extensive earnings smoothing.

@@

### Smoothing and the Correlation Between Changes in Accounting Accruals and Operating Cash Flows (EM2)
EM2 is designed to capture the extent to which insiders use accounting discretion to smooth reported earnings by examining the correlation between changes in accruals and changes in operating cash flows. A stronger negative correlation between these variables indicates that accruals are being used to buffer the impact of cash flow fluctuations, potentially masking the true economic performance of the firm.

@@

4. Calculate EM2, which is computed as the Spearman correlation between these scaled changes, aggregated at the country level over the pooled set of firms within each country, meaning that the correlation reflects the aggregated relationship between changes in accruals and changes in CFO across all firms in that country:
$$
\text{EM2} = \rho\left(\frac{\Delta \text{Accruals}_{it}}{\text{Total Assets}_{i(t-1)}}, \frac{\Delta \text{CFO}_{it}}{\text{Total Assets}_{i(t-1)}}\right)
$$

### Discretion in Reported Earnings: The Magnitude of Accruals (EM3)
EM3 is a measure that obtains the degree of discretion that insiders exercise when reporting earnings, particularly when it comes to misstating a firm’s economic performance. It focuses on the magnitude of accruals as a proxy for earnings management. Insiders can use accruals to overstate or understate earnings, thereby achieving certain financial targets or presenting a skewed view of the firm’s performance.

2. Calculate the absolute values of accruals and CFO for each firm-year.

3. EM3 is calculated as the country-level median ratio of the absolute value of firms’ accruals to the absolute value of their cash flow from operations (CFO). This ratio is used as it scales the magnitude of accruals to a measure of the firm’s size and performance, allowing for comparison across firms of different sizes and performance levels:
$$
\text{EM3} = \text{Median}\left(\frac{|\text{Accruals}_{it}|}{|\text{CFO}_{it}|}\right)
$$
